Simulation Study: Varying Informativeness (smooth)

### 2018-08-31 datasets/simulations/simulations-varyinginformativeness-smooth.Rmd
Fix varying info output file name

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-benchmark-level100.rds")

>>>>

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-smooth-benchmark-level100.rds")
